\section{Experience}
\subsection{Industry}
\block
  {Software Development Engineer Intern}
  {May 2017 -- August 2017}
  {Amazon.com, Inc.}
  {Seattle, Washington}
  {}
  {
    Intern in Amazon's Core Machine Learning team. Aided in the development
    of a scalable internal platform for scientists and engineers that
    streamlines the process of accessing and analyzing large data sources,
    statistical modeling, and machine learning. This included full-stack
    development in Scala and React.js, working with several AWS services, and
    building ML models using various open source libraries.
  }

\subsection{Selected Undergraduate Research}
\block
  {Active Learning for Top-\boldmath$K$ Rank Aggregation from Noisy Comparisons}
  {January 2017 -- Present}
  {University of Minnesota -- Department of Electrical \& Computer Engineering}
  {Minneapolis, Minnesota}
  {Advisor: \href{\soheil}{Soheil \textsc{Mohajer}}}
  {
    Development, analysis, and implementation of an efficient active learning
    algorithm for top-$K$ rank aggregation that ranks items from noisy pairwise
    comparisons.  This work was initially supported by a UROP award and is
    currently supported by a UGRA appointment.
  }

\block
  {MP3: A More Efficient Private Presence Protocol}
  {January 2016 -- September 2017}
  {University of Minnesota -- Department of Computer Science \& Engineering}
  {Minneapolis, Minnesota}
  {Advisor: \href{\hoppernj}{Nicholas \textsc{Hopper}}}
  {
    Developed and implemented an efficient \emph{privacy-preserving}
    cryptographic presence protocol. The notion of presence protocol is for one
    to advertise to their `buddies' if they are online. This is usually
    implemented such that the `central server' knows the entire social graph of
    the service. We proposed MP3---the Minnesota Private Presence Protocol---an
    efficient presence protocol that leaks no information about the social graph
    and maintains forward/backward security in the event of a compromise of the
    infrastructure.  This work was initially supported by a UROP award and was
    later supported by a UGRA appointment. An arXiv preprint of this work is
    currently available.
  }

\subsection{Teaching}
\block
  {Undergraduate Teaching Assistant}
  {Spring 2016 -- Present}
  {University of Minnesota -- Department of Computer Science \& Engineering}
  {Minneapolis, Minnesota}
  {}
  {
    TA for CSCI 1933/1933H, Introduction to Algorithms and Data
    Structures, the second course in computer science. The duties of this
    appointment include:
    \begin{itemize}
      \item Co-leading two 2-hour lab sections each week
      \item Holding weekly office hours
      \item Grading labs, projects, and exams
      \item Working with other TAs to design labs and projects
    \end{itemize}
  }

  % FIXME need to use vspace h4xing because of the itemize and I don't know why
  \vspace{-1em}
